NumLin: Linear Types for Linear Algebra

### 2018-10-28 write-up/paper/implementation.tex
Add section on OCaml 'optimisation'

We actually use this fact to our advantage to clean up the output OCaml by
removing what would otherwise be redundant re-bindings.  Combined with a
code-formatter, the resulting code is not obviously correct and exactly what an
expert would intend to write by hand, but now with the guarantees and safety of
\lang\ behind it. A small example is shown in Figure~\ref{fig:ocaml_sumarray},
a larger one in Figure~\ref{fig:ocaml_kalman}.

>>>>

We actually use this fact to our advantage to clean up the output OCaml by
removing what would otherwise be redundant re-bindings
(Figure~\ref{fig:lang_optimise}).  Combined with a code-formatter, the
resulting code is not obviously correct and exactly what an expert would intend
to write by hand, but now with the guarantees and safety of \lang\ behind it. A
small example is shown in Figure~\ref{fig:ocaml_sumarray}, a larger one in
Figure~\ref{fig:ocaml_kalman}.

\begin{figure}[t]
\begin{center}
    \begin{tabular}{rcl}
        \alsocell[b]{l}{\highl{let Many x = x in} \\
        \highl{let Many x = Many (Many x) in <exp>} } &
        $\Rightarrow$ &
        \highl{<exp>}
    \\ \\
        \alsocell[c]{l}{\highl{let Many x = <exp> in} \\
            \highl{let Many x = Many (Many x) in <body>} \\
            \textbf{OR} \highl{let Many x = Many <exp> in <body>} \\
            \textbf{OR} \highl{(fun x : t -> <body>) <exp>}} &
        $\Rightarrow$ &
        \highl{let x = <exp> in <body>}
    \\ \\
        \alsocell[c]{l}{\highl{(* fixp = fix (f, x:t, <exp> : t') *)} \\
            \highl{let Many f = Many fixp in <body>} \\
            \textbf{OR} \highl{let f = fixp in <body>} } &
        $\Rightarrow$ &
        \highl{let rec f x = <exp> in <body>}
    \end{tabular}
\end{center}
\caption{Removing redundant re-bindings during tranlation to OCaml.}\label{fig:lang_optimise}
\end{figure}
